---
title: "DebugWithinRMarkdown"
author: "Rob Donald"
date: "`r format(Sys.time(), '%A %d %B %Y, %H:%M')`"
output:
  html_document:
    toc: yes
    toc_depth: 3
    toc_float: yes
params:
  dataprep: no
header-includes: \usepackage{comment}
---
<style>
pre {
  overflow-x: auto;
}
pre code {
  word-wrap: normal;
  white-space: pre;
}
</style>


# Introduction

This document is the top level that pulls together several scripts and functions.


See the files:

+ **DebugFunctions.R** simple functions 
+ **Something else**

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,fig.height=8,fig.width=12)
options(width=1500)
```

# Cross platform operation

Demo the techniques I use to cope with Windows support.

```{r system_setup, echo=FALSE}
os.type<-Sys.info()[1]
if(os.type == 'Windows'){TLC_Root<-'C:/PostDocStuff'}else{TLC_Root<-'/Users/rob/PostDocStuff/teaching/RStuff'}
```

# Conditional markdown text

`r if(!params$dataprep) {"\\begin{comment}"}`
## Libraries
`r if(!params$dataprep) {"\\end{comment}"}`

```{r library_setup,include=params$dataprep}
suppressMessages({suppressWarnings({
  library(dplyr)
  library(tidyr)

  library(ggplot2)
  library(ggpmisc)
  library(grid)
  library(gridExtra)
  
  library(RobsRUtils)
  library(futile.logger)
  
  library(data.table)
})})
```

# Background

I have using the RStudio debugger to be one of the weakest bits of the transition to RStudio 
from something like MATLAB. This project is my attempt to explore how it works and see if I can
wrap my head around it enough to teach it to other folk.

## Data Source

Let's use some publically accessible data set. Even better let's use one of the data
sets that are built into R.

This next command will flash up another tab (called R data sets) with a list of all the built in data sets.
```{r}
data()
```

